The framing of active school travel in Ontario, Canada as a health and built environment issue

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.tex
Fixed an error in the references that prevented the Rmd file AST-framing-Ontario from knitting

  \journal{Journal of Transport \& Health} % Sets Journal name

@@

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How do school travel planning stakeholders frame active school travel in Ontario, Canada?},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc citation processing

@@

  \title{How do school travel planning stakeholders frame active school travel in
Ontario, Canada?}
    \author[Some Department]{Author 1\corref{1}}
   \ead{author1@example.com} 
    \author[Some Department]{Author 2}
   \ead{author2@example.com} 
    \author[Another University]{Author 3\corref{2}}
   \ead{author3@example.com} 
    \author[Some Institute]{Author 4\corref{2}}
   \ead{author4@example.com} 
    \author[Some University]{Author 5}
   \ead{author5@example.com} 
    \author[Some Department]{Author 6}
   \ead{author6@example.com} 
      \address[Some Department]{Department, Street, City, Province, Postal Code}
    \address[Another University]{Department, Street, City, Province, Postal Code}
    \address[Some Institute]{Street, City, Province, Postal Code}
    \address[Some University]{Department, Street, City, Province, Postal Code}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Walking and bicycling to school, commonly known as active school travel
(AST), has been declining in Canada and North America for decades
({\textbf{???}}), with levels much lower than other developed countries
like The Netherlands ({\textbf{???}}) and Japan ({\textbf{???}}). In
response to this trend, school travel planning has become a popular
intervention across Canada that has resulted in mixed success with some
schools reporting an increase in AST (e.g., {\textbf{???}}; Mammen et
al., 2014), while others did not observe a change in behaviour
(Buttazzoni et al., 2019) or needed more time and resources to be
effective ({\textbf{???}}).

School travel planning (STP) is a ``school-specific'' intervention led
by a facilitator that brings together a committee of stakeholders from
diverse sectors including education, planning, transportation, and
public health to develop action plans ({\textbf{???}}). This five-step
process involves identifying barriers to AST based on the local context
and implementing approaches or activities that alleviate concerns and
encourage AST ({\textbf{???}}). STP facilitators and committee members
generally intervene at the school through a range of activities such as
educational strategies, in-person events or programs, improvements to
the school site, and enforcement (Mammen et al., 2014).

How STP is framed to a target audience may influence how this
intervention is received and whether it encourages the audience to
support it or participate. In particular, STP stakeholders make choices
about the points of intervention and potential benefits that ought to be
communicated to the public to facilitate adoption of AST. Educational
strategies, which account for approximately one quarter of STP
strategies implemented at Canadian schools (Mammen et al., 2014), need
to effectively engage multiple audiences -- parents, students,
politicians -- on the issue, challenges, and benefits of AST.
Promotional materials, therefore, should reflect current knowledge from
research about school travel and the built environment, as well as local
content specific to factors that influence travel decisions for parents,
in order to effectively engage the public in advocating for improving
AST or to expose parents and the community to essential information that
may prompt behaviour change.

On the one hand, parents have been found to express different
understandings, nomenclature, and conceptualizations than planners of
the factors that influence school travel (Buliung et al., 2021).
However, it is unknown to what degree there is concurrence between STP
materials presented to the public and the literature on school travel
and parental perceptions, and how the complexity of the AST issue is
presented to the public.

The aim of this paper is to fill this research gap by analyzing how AST
is framed by STP stakeholders in Ontario, Canada. We used text mining
and topic modelling to examine how local policy documents from Ontario
municipalities and school boards present and communicate the benefits
and barriers of AST and the solutions for improving AST. We compared the
findings from these documents to a selection of studies on AST and
explored the extent to which there is concurrence between research
findings to date and promotional materials shared with the public to
increase AST.

@@

@@

We assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) school boards (public and English-speaking
only); ii) municipal governments; and iii) transportation consortia.
Non-profit organizations, police services, and advocacy groups are other
stakeholders who may play a role in supporting AST and/or STP, but this
study does not include any documents from these groups because they are
not consistently participating in all initiatives.

The search was guided first by a list of all English public school
boards across Ontario. The websites of each school board were manually
searched for pages related to school transportation or travel. Any pages
relevant to these topics were manually downloaded. Next, we collected
documents by searching municipal government and transportation consortia
websites. The latter were identified based on geographic area (i.e., the
municipalities and/or transportation consortia that are in the same
geographic area of each school board). Pages related to active or school
travel were manually downloaded. Webpages from STP stakeholder websites
were included in our analysis if they were easy to find. This primary
criteria was important since our analysis pertains to how such issues
are framed to the public. Thus, we included only webpages that were easy
to find, which we defined as requiring no more than 2-4 separate links
from the initial Google search.

The initial corpus of policy documents included 64 relevant webpages
(i.e., one page or more) from all STP stakeholder groups. It is
important to note that school boards, municipalities, and transportation
consortia may or may not publish information about their involvement in
AST and STP efforts on their respective websites or in policy documents,
which means that some of these groups for particular regions in Ontario
are not included in our analysis. Search results are summarized in Table
\ref{tab:policy-documents}.

@@

\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}l|l|>{}l}
\toprule
Stakeholder & Total & Included\\
\midrule
\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{31}\\
\textbf{Municipalities} & 62 & 25\\
\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{8}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{academic-papers}{%
\subsubsection{3.2.1. Academic papers}\label{academic-papers}}

@@

A multi-step process was conducted to ensure that the analysis captured
as much content as possible from both the policy documents (n = 64) and
academic papers (n = 233). To begin, the webpages, which were manually
downloaded in portable document format (PDF), were trimmed so that pages
that only consisted of tables, figures, or references were removed. Many
academic papers were in a two-column format, which is not ideal for
conversion to \texttt{txt}. We adapted a procedure
(https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r)
to read the two-column PDF documents so that they would be converted
correctly. Four academic papers did not join sufficiently and were taken
out of the corpus due to the substantial time required to manually
correct their inconsistencies.

Next, we converted the trimmed PDF documents into \texttt{txt} files so
that they could be imported in R for analysis. We then proceeded to a
manual cleaning phase where we removed any remaining tables, figures,
references, headers/footings, and captions that could not be trimmed.
Manual corrections were also required for certain pages in academic
papers that remained in two-column format after the conversion process.
This typically occurred on pages that had a table or figure which
disrupted the text. Finally, we reviewed all of the documents to remove
hyphenation by line breaks and to keep hyphenated words together on the
same line. Any ligatures (e.g., combinations of characters or letters
that were not properly detected during the conversion process) were
fixed by inserting the unicode sequence of character to replace the
missing sequence of characters.

@@

In the final step, we removed all blank spaces, punctuation,
capitalization, and numbers. English stop words, which are common words
such as \emph{and} or \emph{the} as identified in a predetermined list
by Lewis et al.~({\textbf{???}}) and other frequent terms in the
documents like ``school'' and specific location names, were removed from
the corpora.

@@

Issues that pertain to public health or wellbeing are often presented to
the public through particular frames to influence perceptions or
behaviours. Gamson and Modigliani ({\textbf{???}}) conceptualize a frame
as a ``central organizing idea or story line that provides meaning'' to
a particular phenomenon. A frame can enable individuals ``to locate,
perceive, identify, and label'' information pertaining to various
dimensions of an issue (Goffman, 1974). Scholars in the field of
political communications have proposed that communicators, such as the
media or an institution, construct the narrative of a frame for policy
positions or public issues in order to activate or restrict a particular
response in the intended audience (Pan and Kosicki, 1993). Framing can
be used to position existing solutions as suitable to address particular
issues (Mah et al., 2014), which may prevent the public from being aware
of other policy approaches that challenge the status quo to bring about
more radical change. The way policy issues are framed is ultimately
important to understand because it plays a role in either altering or
preserving the existing social perceptions.

Framing of issues is an important step in developing health policy. An
obvious example over the past decade is the framing of climate change as
a public health issue (e.g., @ depouxCommunicatingClimateChange2017;
Maibach et al., 2010; Weathers and Kendall, 2016) to increase public
engagement and reception of the issue. Transport planners also use
different frames to guide the extent to which transport policies can be
adapted to address climate change. In a recent paper ({\textbf{???}}),
framing analysis was applied to review the representation of issues such
as mobility and social exclusion in municipal policies from four western
Canadian cities under the current circumstances of climate change. The
authors found four primary frames: ``The Growing City'', ``If You Build
It, They Will Come'', ``Better City for All'', and a ``the Resilient
City''. Each frame presented the nature, opportunities, and challenges
of climate change in different ways which set the stage for the types of
mitigation and adaptation strategies that cities were proposing to
address this issue.

Given the range of factors at multiple levels of the socioecological
model that influence school travel, it is important to understand how
walking and bicycling to school are framed to the public. Is active
school travel framed as a public health or environmental issue? Is it
framed as both? Do proposed solutions to increase AST focus primarily on
the intrapersonal and interpersonal factors, meaning that behaviour
change must ultimately result from different decisions made by the
individual or the household? Or is the decline in AST framed as an issue
that must be addressed through changes in the built environment? These
are the types of questions that we aim to answer in this paper. To our
knowledge, this topic has not be addressed in the school travel
literature to date.

@@

This paper is an example of open and reproducible research that uses
only open software. All data were obtained from publicly available
sources and organized in the form of a data package. Following best
practices in spatial data science ({\textbf{???}}), the code and data
needed to reproduce or conduct a similar analysis for other regions in
North America or elsewhere are available for download.

@@

\caption{Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
\end{figure}

@@

\caption{Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
\end{figure}

@@

\caption{Most common bigrams found in the school board documents.}\label{fig:school-visual}
\end{figure}

@@

\caption{Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
\end{figure}

>>>>

  \journal{Social Science \& Medicine} % Sets Journal name

@@

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={The framing of active school travel in Ontario, Canada as a health and built environment issue},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

  \title{The framing of active school travel in Ontario, Canada as a
health and built environment issue}
    \author[Some Department]{Author 1\corref{1}}
   \ead{author1@example.com} 
    \author[Some Department]{Author 2}
   \ead{author2@example.com} 
    \author[Another University]{Author 3\corref{2}}
   \ead{author3@example.com} 
    \author[Some Institute]{Author 4\corref{2}}
   \ead{author4@example.com} 
    \author[Some University]{Author 5}
   \ead{author5@example.com} 
    \author[Some Department]{Author 6}
   \ead{author6@example.com} 
      \address[Some Department]{Department, Street, City, Province,
Postal Code}
    \address[Another University]{Department, Street, City, Province,
Postal Code}
    \address[Some Institute]{Street, City, Province, Postal Code}
    \address[Some University]{Department, Street, City, Province, Postal
Code}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

Rates of walking and bicycling to school, commonly known as active
school travel (AST), have been declining in Canada and the United States
for decades (\textbf{rothmanDeclineActiveSchool2018?}), with levels much
lower than other developed countries like The Netherlands
(\textbf{vangoeverdenSchoolTravelBehaviour2013?}), Denmark
(\textbf{jensenHowObtainHealthy2008?}), and Japan
(\textbf{waygoodChapterSixteenJapan2020?}). However, the appetite for
AST may be high in many Canadian communities. For instance, 40\% of
children in a study conducted in Toronto, Ontario who are driven to
school would like to travel by bicycle instead
(\textbf{laroucheRatherBikeSchool2016a?}). But the study reported that
less than 3\% actually do, despite the vast majority having access to a
bicycle and living within a short and bikeable distance to school.
Another study based in London, Ontario reported similar findings with
respect to children's preference for active travel
(\textbf{larsenRouteBasedAnalysisCapture2012?}). From a public health
perspective, this represents a huge opportunity to improve health and
wellbeing if more children could use active modes to school.

In response to this trend, the Government of Ontario, in Canada, created
a fund in 2017 to support communities across the province in developing
AST initiatives. Green Communities Canada runs the program, called
\emph{Ontario Active School Travel}, and determines the projects that
will be funded with their support (\textbf{GreenCommunities2016?}). As
of December 2021, OAST has funded and provided resources for over 20
projects across Ontario. Many communities implemented school travel
planning (STP), along with encouragement activities like walking school
buses or developed resources for schools and parents, among other
actions (see \textbf{GreenCommunitiesProjects?}). In this context, STP
is a popular ``school-specific'' intervention led by a facilitator that
brings together a committee of stakeholders from diverse sectors
including education, planning, transportation, and public health to
develop action plans (\textbf{buliungSchoolTravelPlanning2011?};
\textbf{mammenSchoolTravelPlanning2014?}). The five-step process
involves identifying barriers to AST based on the local context and
implementing approaches or activities following the 5 E's that alleviate
concerns about AST and make AST safer and more convenient
(\textbf{buliungSchoolTravelPlanning2011?};
\textbf{langUnderstandingModalChoice2011?}).

How AST is framed by STP stakeholders to a target audience, like parents
or the general public, may raise awareness about the issue and influence
how walking and bicycling to school are perceived. Gamson and Modigliani
(\textbf{gamsonChangingCulture1987?}) define a frame as a ``central
organizing idea or story line that provides meaning'' to a particular
phenomenon. A frame can enable individuals ``to locate, perceive,
identify, and label'' information pertaining to various dimensions of an
issue (Goffman, 1974). Therefore, stakeholder groups involved in STP
efforts can play a role in shaping public perception about AST in such a
way that it attracts greater attention and becomes a ``problem'' that
needs to be addressed through behaviour change or by new policies. We
also contend that the ways in which the AST issue is framed can affect
the policy process, as outlined in Kingdon's
(\textbf{kingdonAgendasAlternativesPublic1984?}) Multiple Streams
Framework (MSF), through all three streams (i.e., problem, policy, and
politics). This framing can ultimately impact financial contributions
and potential solutions to address the decline of AST in Canada.

After significant investment of human and financial resources to boost
rates of AST in Ontario over the past few years, we ask the following
questions: How is AST framed? What benefits of AST are communicated to
the public? What solutions are proposed to increase rates of AST? Do
proposed solutions focus primarily on the intrapersonal and
interpersonal factors, meaning that behaviour change must ultimately
result from the individual or household making different travel
decisions? Or is AST framed as an issue that must be addressed through
changes in the built environment or at the policy level?

In this paper, we use text mining and topic modelling to examine how
three STP stakeholder groups in Ontario (i.e., municipalities, school
boards, and transportation consortia) frame the issue of AST. We
assembled a corpus of texts from webpages that can be considered an
important source of information for the general public or parents who
are interested in AST. We examine word frequency, bigrams, and
concordances in these selected documents, and also identify key topics
presented by each stakeholder group. We then compare the findings from
these documents to a selection of studies on AST and explore the extent
to which there is concordance between the literature on AST and
materials shared with the public.

@@

\hypertarget{benefits-of-active-school-travel}{%
\subsection{2.1. Benefits of active school
travel}\label{benefits-of-active-school-travel}}

The benefits of AST are valuable information to communicate to the
public in order to convey the importance of this issue. The desire to
increase AST in Canada is certainly warranted - there is compelling
evidence that children who actively commute to school earn physical and
mental health benefits. Faulkner et al. (2009) concluded from their
systematic review that children who travel on foot or by bicycle to
school generally have higher levels of physical activity than their
peers who are driven to school. However, Schoeppe et al. (2015) reported
no association between AST and physical activity. This relationship
could be dose-dependent, meaning that children would have to travel
longer distances to accumulate physical activity. A walking distance of
1000-1600 metres to school has been found to contribute to overall
levels of physical activity for boys
(\textbf{faulknerSchoolTravelChildren2013?}). The daily routine of
travelling to school can be a good opportunity for children to regularly
build physical activity into their schedule
(\textbf{mitraIndependentMobilityMode2013?}). Research has also shown
that using active modes to school contributes to improvements in
cardiovascular fitness
(\textbf{borrestadExperiencesRandomisedControlled2012?}).

More recently, there has been literature exploring the link between
transport and children's wellbeing
(\textbf{waygoodTransportChildrenWellbeing2020?}), with relevant
applications to the study of travel satisfaction (van den Berg et al.,
2020; \textbf{westmanChildrenTravelSchool2017?}). Being driven to school
reduces community interactions for children which may impact their
social wellbeing (\textbf{waygoodChildrenTravelIncidental2015?}),
whereas walking and bicycling give children opportunities to socialize
with friends or siblings
(\textbf{michailChildrenExperiencesTheir2021?}). This is something that
children highly value about travel
(\textbf{zwertsHowChildrenView2010a?}) and indicates that social
connections through travel are important for their wellbeing. AST also
provides opportunities for children to engage with the natural
environment (\textbf{fuscoUnderstandingChildrenPerceptions2012?};
\textbf{romeroChildrenExperiencesEnjoyment2015?}) which can improve
their mental or emotional wellbeing.

\hypertarget{factors-that-influence-active-school-travel-and-mode-choice}{%
\subsection{2.2. Factors that influence active school travel and mode
choice}\label{factors-that-influence-active-school-travel-and-mode-choice}}

Factors that influence AST have been presented and organized using a
socio-ecological model (SEM)
(\textbf{mitraIndependentMobilityMode2013?}) or systems model
(\textbf{badlandDevelopmentSystemsModel2016?}) whereby children's travel
behaviour is understood within the context of their household, social,
neighbourhood, and policy environments. Individual characteristics of
the child are also determinants. The SEM comes from the field of public
health and is a useful framework for understanding complex health
behaviours, including travel habits such as walking or bicycling to
school, because it identifies multiple determinants that need to be
addressed by interventions to facilitate behaviour change. The consensus
in the literature is that various factors are interrelated and that
interventions should target multiple levels in order to increase levels
of healthy and physically active modes of travel to school
(\textbf{mitraIndependentMobilityMode2013?}). Rather than describing an
extensive list of factors that influence AST and mode choice in Canada,
which has been covered elsewhere (e.g., Mammen et al., 2012; Wilson et
al., 2018; \textbf{mitraIndependentMobilityMode2013?};
\textbf{rothmanDeclineActiveSchool2018?}), we briefly discuss a few
potentially modifiable determinants that may be targeted for change
through STP.

At the individual level, older child age is often associated with AST
(Mammen et al., 2012; Wilson et al., 2018;
\textbf{starkExploringIndependentActive2018?}) as parents typically
escort younger children. There is some evidence that gender is a
determinant of AST (\textbf{larsenInfluencePhysicalEnvironment2009?}),
with boys being more likely to travel using active modes than girls,
although this is not a strong or consistent finding (Schoeppe et al.,
2015; \textbf{rothmanDeclineActiveSchool2018?}). Children's mode choice
to school is strongly influenced by their parents' travel behaviours and
the complexity of their household's travel needs (Buliung et al., 2021),
which indicates that shifting parental perceptions and habits is
important. Convenience and inclement weather have been cited by parents
as barriers to AST (\textbf{buliungSchoolTravelPlanning2011?}). Parental
perceptions of the built or school environment (De Meester et al., 2014;
Panter et al., 2010) and their children's skills (Ghekiere et al., 2017)
also influence whether they allow their children to walk or bicycle to
school.

Distance between home and school is most strongly associated with AST
(Ikeda et al., 2018; Mammen et al., 2012; Pont et al., 2009;
\textbf{rothmanDeclineActiveSchool2018?}) with less AST reported among
children who have to travel farther to school. Many studies have also
found that the quality of the built environment along the route to
school and around the school site (Ikeda et al., 2018; Kim and Lee,
2020; \textbf{rothmanActiveSchoolTransportation2021?}) and provision of
active travel infrastructure (Pont et al., 2009;
\textbf{chenPromotingActiveStudent2018a?}) facilitate AST. Canadian
youth report that they feel most safe bicycling on streets in their
neighbourhood or that have low volumes of traffic
(\textbf{TACbikeinfra2020?}). Finally, concerns about traffic and
strangers have been reported by parents who drive their children to
school (Mammen et al., 2012), which highlights that the volume and speed
of cars can be a concern or deterrent for AST.

\hypertarget{school-travel-planning-in-canada}{%
\subsection{2.3. School travel planning in
Canada}\label{school-travel-planning-in-canada}}

School travel planning (STP) has been implemented in Canada since at
least the late 2000s. Within the STP process, facilitators generally
establish multi-sector committees who intervene at the participating
school through a range of activities related to the 5E's such as
\emph{education} strategies, \emph{encouragement} through in-person
events or programs, \emph{engineering} improvements to or around the
school site, and \emph{enforcement} of traffic speeds around schools
(Mammen et al., 2014; \textbf{langUnderstandingModalChoice2011?}). The
first large-scale evaluation of STP as an intervention in Canada took
place at twelve schools across the country, including four in Ontario,
using parental surveys to measure changes in travel behaviour and
perceptions (\textbf{buliungSchoolTravelPlanning2011?}). Since then,
there have been other assessments of both the efficacy of STP
(Buttazzoni et al., 2019; Mammen et al., 2014) and the process of
implementing such programs in Ontario (Buttazzoni et al., 2018;
\textbf{mammenPuttingSchoolTravel2015?}). STP facilitators have
recommended that additional time and resources are needed to improve the
efficacy of STP (\textbf{mammenPuttingSchoolTravel2015?}), which
highlights that long-term and sustained efforts driven at the policy
level are required to address declining rates of AST.

The ways in which AST is framed seem particularly important to shift
parental attitudes and perceptions given their reported influence on
children's travel mode to school. STP activities heavily focus on
education or encouragement (Buttazzoni et al., 2018; Mammen et al.,
2014; \textbf{buliungSchoolTravelPlanning2011?}), but parents may not
always be receptive to the goals of STP and may be resistant to
behaviour change (see Buttazzoni et al., 2018). Parents have been found
to express different understandings, language, and perceptions than
planners of the built environment determinants that influence school
travel (Buliung et al., 2021). This is also true when it comes to other
factors like convenience of different modes to school
(\textbf{langUnderstandingModalChoice2011?}). STP stakeholder groups
must pay special attention to parents' understanding of the decline of
AST as a problem, which may affect their receptivity to proposed
solutions.

The ``central organizing idea or story line'' of AST, to apply the
definition from Gamson and Modigliani
(\textbf{gamsonChangingCulture1987?}), could also affect broader support
in the community. Municipal representatives are perceived to be
instrumental but the involvement of other stakeholder groups (e.g.,
busing consortium representatives and local residents) can be lacking
(Buttazzoni et al., 2018). In Ontario, it would be reasonable to say
that AST has become a policy issue on the education and public health
agendas over this time as evidenced by the financial contribution from
the provincial government. The support from a range of municipal
representatives (see Buttazzoni et al., 2018;
\textbf{mammenPuttingSchoolTravel2015?}) demonstrates that the ``policy
stream'' (see \textbf{kingdonAgendasAlternativesPublic1984?}) has been
well engaged. It is unknown to what degree the general public (i.e.,
local residents) has been exposed to messaging about AST, which could
affect their participation in the STP process as desired by STP
facilitators (Buttazzoni et al., 2018).

The success of STP interventions would likely depend on parental
judgments of factors that are related to school travel, as well as
support from key policy makers. For example, parents have been found to
view mixed land use as conducive for driving, despite transport planners
viewing neighbourhoods with mixed uses as key for encouraging more
active travel (Buliung et al., 2021). Therefore, stakeholder groups
involved in STP must make important choices about the proposed solutions
and potential benefits that ought to be communicated to parents and the
general public about AST to convey its importance as a policy issue and
to facilitate adoption of AST. Publicly available content about AST,
therefore, needs to effectively engage multiple audiences on this policy
issue including parents, children, politicians, and school
representatives. This information should reflect current knowledge from
research on school travel, plus content specific to local factors that
influence AST, so that the challenges of AST are adequately defined and
the opportunities or solutions to address the problems are clear.
However, it is unknown to what degree STP materials presented to the
general public reflect the scope of evidence from the literature on AST.

@@

We assembled a collection of publicly available documents that were
sourced online from the main stakeholder groups involved in STP
initiatives in Ontario: i) school boards (public or Catholic and
English-speaking only); ii) municipal governments; and iii)
transportation consortia. The latter are a unique group of entities
sanctioned by Ontario's Ministry of Education in Ontario 2006. Each
consortium involves a collaboration between regions and school boards;
the consortium's objective is to deliver more efficient and timely
transportation services to schools in each region
(\textbf{ministryeducation2006?}). Non-profit organizations, police
services, and advocacy groups are other stakeholders who often play a
role in supporting AST and/or STP, but this study does not include any
documents from these groups because they are not consistently
participating in all initiatives across Ontario.

The search was guided first by a list of all English public and Catholic
school boards across Ontario. The websites of each school board were
manually searched for pages related to school transport or travel. Any
pages relevant to these topics were manually downloaded. Next, we
collected documents by searching municipal government and transportation
consortia websites. These were identified based on geographic area
(i.e., the municipalities and/or transportation consortia that are in
the same geographic area of each school board). Webpages related to
active transport or school travel were manually downloaded.

Webpages from STP stakeholder groups were included in our analysis if
they were easy to find. This primary criterion was important since our
analysis pertains to how such issues are framed to the general public.
Thus, we included only webpages that were readily accessible, which we
defined as requiring no more than 2-4 separate links from the initial
Google search.

The initial corpus of documents from STP stakeholder groups included 69
relevant webpages (i.e., one page or more) from all STP stakeholder
groups. We refer to these as policy documents throughout the paper. It
is important to note that school boards, municipalities, and
transportation consortia may or may not publish information about their
involvement in AST and STP efforts on their respective websites or in
policy documents. Search results are summarized in Table
\ref{tab:policy-documents}.

@@

\caption{\label{tab:policy-documents}\label{tab:search-results}Search results from the main STP stakeholder groups.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}l|l|>{}l}
\toprule
Stakeholder & Total & Included\\
\midrule
\cellcolor{gray!6}{\textbf{School boards}} & \cellcolor{gray!6}{62} & \cellcolor{gray!6}{32}\\
\textbf{Municipalities} & 62 & 28\\
\cellcolor{gray!6}{\textbf{Transportation consortia}} & \cellcolor{gray!6}{39} & \cellcolor{gray!6}{9}\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{academic-papers}{%
\subsubsection{3.1.2. Academic papers}\label{academic-papers}}

@@

A multi-step process was conducted to ensure that the analysis captured
as much text as possible from both the policy documents (n = 64) and
academic papers (n = 233). To begin, the webpages, which were manually
downloaded in portable document format (PDF), were trimmed so that pages
that only consisted of tables, figures, or references were removed. Many
academic papers were in a two-column format, which is not ideal for
conversion to \texttt{txt}. We adapted a procedure
(https://stackoverflow.com/questions/42541849/extract-text-from-two-column-pdf-with-r)
to read the two-column PDF documents so that they would be converted
correctly. Four academic papers did not join sufficiently and were taken
out of the corpus due to the substantial time required to manually
correct their inconsistencies.

Next, we converted the trimmed PDF documents into \texttt{txt} files so
that they could be imported in R for analysis. We then proceeded to a
manual cleaning phase where we removed any remaining tables, figures,
references, headers/footings, and captions that could not be trimmed.
Manual corrections were also required for certain pages in academic
papers that remained in two-column format after the conversion process.
This typically occurred on pages that had a table or figure which
disrupted the text. Finally, we reviewed all of the documents to remove
hyphenation by line breaks and to keep hyphenated words together on the
same line. Any ligatures (e.g., combinations of characters or letters
that were not properly detected during the conversion process) were
fixed by replacing the unicode sequence of character by inserting the
missing sequence of characters.

@@

In the final step, we removed all blank spaces, punctuation,
capitalization, and numbers. English stop words, which are common words
such as \emph{and} or \emph{the} as identified in a predetermined list
by Lewis et al. (\textbf{R-tm?}) and other frequent terms in the
documents like ``school'' and specific location names, were removed from
the corpora.

@@

Issues that pertain to public health or wellbeing are often presented to
the public through particular frames to influence perceptions or
behaviours. As previously mentioned, a frame is a ``central organizing
idea or story line that provides meaning'' to a public issue or
phenomenon (\textbf{gamsonChangingCulture1987?}). Scholars in the field
of political communications have proposed that communicators, such as
the media or an institution, construct the narrative of a frame for
policy positions or public issues in order to activate or restrict a
particular response in the intended audience (Pan and Kosicki, 1993).
Organized groups of stakeholders can employ similar methods to attract
attention to particular issues. Framing can be used to position existing
solutions as suitable to address particular issues (Mah et al., 2014),
which may prevent the public from being aware of other policy approaches
that challenge the status quo. The way policy issues are framed is
ultimately important to understand because it plays a role in either
altering or preserving the existing social perceptions. This, in turn,
can affect whether issues are put on the agenda of policy makers and can
determine which solutions are proposed to address the problem
(\textbf{kingdonAgendasAlternativesPublic1984?}).

Framing of issues is an important step in developing health policy. An
obvious example over the past decade is the framing of climate change as
a public health issue (e.g., Depoux et al., 2017; Maibach et al., 2010;
Weathers and Kendall, 2016) to increase public engagement and awareness
of the issue. This framing has slowly advanced this issue on public
policy agendas as public attention puts pressure on the policy stream to
adopt frameworks for action. For example, transport planners also use
different frames to guide the extent to which transport policies can be
adapted to address climate change. In a recent paper
(\textbf{reynardGrowthResilienceHow2021?}), framing analysis was applied
to review the representation of issues such as mobility and social
exclusion in municipal policies from four western Canadian cities under
the current circumstances of climate change. The authors found four
primary frames: ``The Growing City,'' ``If You Build It, They Will
Come,'' ``Better City for All,'' and a ``the Resilient City''
(\textbf{reynardGrowthResilienceHow2021?}). Each frame presented the
nature, opportunities, and challenges of climate change in different
ways which set the stage for the types of mitigation and adaptation
strategies that cities were proposing to address this issue.

In a similar way, we hypothesize that STP stakeholder groups in Ontario
have framed AST in particular ways to effectively engage multiple
audiences on this policy issue including parents, local residents,
school representatives, and municipal representatives. These groups are
likely identifying points of intervention and potential opportunities to
build support for and encourage AST.

@@

This paper is an example of open and reproducible research that uses
only open software. All data were obtained from publicly available
sources and organized in the form of a data package. Following best
practices in spatial data science (\textbf{brunsdon2020opening?}), the
code and data needed to reproduce or conduct a similar analysis for
other regions in North America or elsewhere are available for download.

@@

\caption{\label{fig:city-visual}Most common bigrams found in the municipal or regional government documents.}\label{fig:city-visual}
\end{figure}

@@

\caption{\label{fig:consortia-visual}Most common bigrams found in the transportation consortia documents.}\label{fig:consortia-visual}
\end{figure}

@@

\caption{\label{fig:school-visual}Most common bigrams found in the school board documents.}\label{fig:school-visual}
\end{figure}

@@

\caption{\label{fig:policy-visual}Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined).}\label{fig:policy-visual}
\end{figure}
